Outstanding Title

### 2017-05-03 writing/EpiDraft.Rmd

```{r, echo=F, warning=F, message=F}
#plot of CDC data
library(ggplot2)

leg_cases[,1:4] %>% 
  gather(key = location, value = cases, - week_end_date) %>% 
  ggplot(aes(x = week_end_date, y = cases, color = location)) + 
  #geom_point() + 
  geom_line() + 
  theme_classic() + 
  theme(legend.position = "top")

@@

```{r}
#Checking for anomalies:
leg_cases[which(leg_cases$checkma != "MID. ATLANTIC"),]
leg_cases[which(leg_cases$checknyc != "N.Y. City"),]
leg_cases[which(leg_cases$checkpa != "Pa."),]

@@

```{r}
library(lubridate)
library(dplyr)
#Precipitation data for New York City and Philadelphia:
parain <- readRDS("~/eesim/writing/data/pa.rds")
nyrain <- readRDS("~/eesim/writing/data/pa.rds")
paquant <- quantile(parain$prcp, probs = c(.75, .95, .99), na.rm=T)
nyquant <- quantile(nyrain$prcp, probs = c(.75, .95, .99), na.rm=T)
parain$quant75 <- ifelse(parain$prcp>paquant[1], 1,0)
parain$quant95 <- ifelse(parain$prcp>paquant[2], 1,0)
parain$quant99 <- ifelse(parain$prcp>paquant[3], 1,0)
nyrain$quant75 <- ifelse(nyrain$prcp>nyquant[1], 1,0)
nyrain$quant95 <- ifelse(nyrain$prcp>nyquant[2], 1,0)
nyrain$quant99 <- ifelse(nyrain$prcp>nyquant[3], 1,0)
parain$month <- month(parain$date)
parain$year <- year(parain$date)
nyrain$month <- month(nyrain$date)
nyrain$year <- year(nyrain$date)
#Monthly rainfall above 75th, 95th, and 99th percentiles for Philly and NYC
pamonthly <- group_by(parain, month, year) %>% summarise(quant75 =mean(quant75), quant95=mean(quant95), quant99=mean(quant99))
nymonthly <- group_by(nyrain, month, year) %>% summarise(mean(quant75), mean(quant95), mean(quant99))
ggplot(pamonthly, aes(x=1:136, y=quant95))+geom_line()
```

@@

```{r}
custom
```

>>>>

```{r, echo=F, warning=F, message=F}
#plot of CDC data
library(rvest)
library(purrr)
library(dplyr)
library(stringr)
library(lubridate)
library(tidyr)
library(ggplot2)

load("~/eesim/writing/data/leg_cases.rda")
leg_cases[,1:4] %>% 
  gather(key = location, value = cases, - week_end_date) %>% 
  ggplot(aes(x = week_end_date, y = cases, color = location)) + 
  #geom_point() + 
  geom_line() + 
  theme_classic() + 
  theme(legend.position = "top")

@@

```{r, echo=F, eval=F}
#Checking for anomalies:
leg_cases[which(leg_cases$checkma != "MID. ATLANTIC"),]
leg_cases[which(leg_cases$checknyc != "N.Y. City"),]
leg_cases[which(leg_cases$checkpa != "Pa."),]

@@

```{r}
library(lubridate)
library(dplyr)
#Precipitation data for New York City and Philadelphia:
parain <- readRDS("~/eesim/writing/data/pa.rds")
nyrain <- readRDS("~/eesim/writing/data/pa.rds")
paquant <- quantile(parain$prcp, probs = c(.75, .95, .99), na.rm=T)
nyquant <- quantile(nyrain$prcp, probs = c(.75, .95, .99), na.rm=T)
parain$quant75 <- ifelse(parain$prcp>paquant[1], 1,0)
parain$quant95 <- ifelse(parain$prcp>paquant[2], 1,0)
parain$quant99 <- ifelse(parain$prcp>paquant[3], 1,0)
nyrain$quant75 <- ifelse(nyrain$prcp>nyquant[1], 1,0)
nyrain$quant95 <- ifelse(nyrain$prcp>nyquant[2], 1,0)
nyrain$quant99 <- ifelse(nyrain$prcp>nyquant[3], 1,0)
parain$month <- month(parain$date)
parain$year <- year(parain$date)
nyrain$month <- month(nyrain$date)
nyrain$year <- year(nyrain$date)
#Monthly rainfall above 75th, 95th, and 99th percentiles for Philly and NYC
pamonthly <- group_by(parain, month, year) %>% summarise(quant75 =mean(quant75), quant95=mean(quant95), quant99=mean(quant99))
nymonthly <- group_by(nyrain, month, year) %>% summarise(mean(quant75), mean(quant95), mean(quant99))
#What pattern is this?
ggplot(pamonthly, aes(x=1:136, y=quant95))+geom_line()+geom_vline(xintercept=seq(from=1, to=136, by=12), col="red") + ggtitle("Monthly rainfall for Philadelphia 2006-2017")+ ylab("Proportion of days over 95th percentile")
```

@@

```{r}
```
